\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Gowtham A} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 99439 99489 \\ Coimbatore, IN} 
\address{\href{mailto:glistengowtham@gmail.com}{glistengowtham@gmail.com} \\ \href{https://www.linkedin.com/in/gowtham-ayyasamy/}{linkedin.com/in/gowtham-ayyasamy/} \\ \href{https://linktr.ee/gowthamayyasamy}{linktr.ee/gowthamayyasamy}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Aspiring AI Engineer and Data Scientist with a strong background in AI, Data Science, and Psychology. Skilled in Python, Flutter, Firebase, machine learning and psychology. Excited to contribute to impactful projects and innovative solutions.}


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Python, JavaScript, Dart, HTML5, CSS, Bootstrap, Flutter, PowerBI, MongoDB, Firebase\\
   & MS Office, Figma, Manual Testing, Git, GitHub, Bitbucket,Flask, Django, Linux, Windows\\
Soft Skills & Problem-solving, Communication, Team collaboration, Adaptability, Critical thinking\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}
\textbf{Freelance Software Developer} \hfill Aug 2024 - Present\\
Qwat.in \hfill \textit{Tamilnadu, IN}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Developed Qwat.in website and blog, reaching 200+ active users/month and publishing 20+ blogs, boosting engagement by 80\%. 
     \item Led projects like The Bus App and Museum Chatbot, achieving 95\% user satisfaction with real-time features. \item Completed image segmentation for Tamil Language dataset with 90\% accuracy; currently developing Furlo pet shop app with AR. 
 
 \end{itemize}
 
\textbf{Software Developer } \hfill Mar 2024 - July 2024\\
iBots.in \hfill \textit{Tamilnadu, IN}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Led Glu project, boosting data scanning speed by 40\% with Bluetooth-controlled scanner devices. 
     \item Developed Dial2Tech, an in-house solution that cut engineer search time by 30 minutes. 
     \item Documented 17+ projects, enhancing clarity and consistency across documentation. 
 \end{itemize}
 
\textbf{Web Development Intern} \hfill Mar 2023 - May 2023\\
Skillbag.in \hfill \textit{Lucknow, IN}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Developed websites using Django framework, enhancing
     user engagement by 30\%.
     \item Automated email process, eliminating manual work by 70\%.
    \item Integrated WhatsApp API for real-time client interaction,
increasing satisfaction by 25\% 
 \end{itemize}

 \textbf{Machine Learning Intern} \hfill Feb 2023 - Mar 2023)\\
Suvidha Foundation \hfill \textit{Maharashtra, IN }
 \begin{itemize}
    \itemsep -3pt {} 
     \item Led Arabic text translation project to 80\% accuracy.
     \item Optimized translation processes, cutting turnaround
time by 40\%.
 \end{itemize}

  \textbf{Game Tester} \hfill Feb 2022 - Sep 2022)\\
K12 Techno Services \hfill \textit{Bangalore, IN }
 \begin{itemize}
    \itemsep -3pt {} 
     \item Conducted rigorous testing protocols, identifying and
reporting 100+ bugs per week.
     \item Collaborated on bug resolution, maintaining a 90\% fix
rate within deadlines.
    \item Enhanced game stability and user experience by providing detailed feedback and recommendations, leading to 30\% improvement in overall game performance.
    \vspace{1em}
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\vspace{10em}
\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Disease Prediction Using Machine Learning} \href{https://github.com/Gowthampsych/Mini-project}{(GitHub)}
\begin{itemize}
    \item {Developed an ML model using Naive Bayes, Decision Tree, and Random Forest algorithms.
    \item Achieved 93\% accuracy for disease prediction, significantly improving early diagnosis and decision-making in medical applications.
     \item Implemented feature engineering and data preprocessing techniques.}
\end{itemize}

\item \textbf{Multiple People and Object Tracking System} \href{https://github.com/Gowthampsych/mini_project_2/tree/master}{(GitHub)}
\begin{itemize}
    \item {Engineered a real-time tracking system using YOLOv7 and StrongSORT, achieving 95\% accuracy in tracking people and objects.
    \item Improved surveillance and monitoring efficiency through advanced object detection capabilities.}
\end{itemize}

\item \textbf{Blockchain-Based DNS Modification Module for Fast Flux} \href{https://github.com/Gowthampsych/dns-modification}{(GitHub)}
\begin{itemize}
    \item {Implemented a blockchain module for 100\% secure DNS modifications.
    \item Achieved 98\% accuracy in detecting malicious websites, enhancing cybersecurity defenses.
     \item Developed a CLI-based solution that provides continuous protection against fast flux attacks.}
\end{itemize}
\end{rSection} 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf B.Tech Artificial Intelligence and Data
Science}, Sri Ramakrishna Engineering
College \hfill {2020 - 2024}\\
Relevant Coursework: Machine learning, Computer Vision, Data Visualization, operating systems.

{\bf B.Sc Psychology}, Tamilnadu Open University \hfill {2020 - 2023} \\
Relevant Coursework: Social Psychology, Cognitive Psychology


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications } 
\begin{itemize}
    \item Overview of Data Visualization \href{https://www.coursera.org/account/accomplishments/verify/9XH2ALR8KBNV}{→}
    \item Fundamentals of Deep Learning \href{https://learn.nvidia.com/certificates?id=e46d86c53f1647bfbc2eebaafbed88bc}{→} 
    \item Red Hat Certified System Administrator \href{https://www.coursera.org/account/accomplishments/verify/9XH2ALR8KBNV}{→} 
    \item Web Development Bootcamp  \href{https://www.mygreatlearning.com/certificate/WQCNEJYZ}{→}
    \item GitHub Tutorial \href{https://www.mygreatlearning.com/certificate/YLGEWEGH}{→}
    \item Blockchain Mastery \href{https://www.udemy.com/certificate/UC-ffd8e16b-7f68-4eeb-9b8f-c2725a95b8a2/}{→}
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
%	PUBLICATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}

{\bf M. Logaprakash, A. Gowtham, S. Madhav, and S. Gokul,} "Blockchain-based DNS Modification Module for Fast Flux," in \emph{Hybrid and Advanced Technologies: Proceedings of ICHAT 2024}, CRC Press, 2025. \\ISBN 9781032906652.\\
\\
{\bf Gowtham A.} (2024).  
\textbf{Blogs on Diverse Topics Including Technology, Lifestyle, Psychology, Business, and Animals}. Qwat Blog.  
Visit: \href{https://blog.qwat.in}{blogs.qwat.in}

\end{rSection}


%----------------------------------------------------------------------------------------
\vspace{4em}
\begin{rSection}{Acknowledgment} 
{I hereby affirm that the information provided in this resume is accurate and complete to the best of my knowledge. All experiences, skills, and qualifications mentioned are true and reflect my actual capabilities and achievements.}
\end{rSection}


\end{document}
